Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-06-11 Documents/M1/realizableFermionicM1/sections/appendix.tex
Added the proof of nonexistence s=3 type A IMEX to the appendix.

>>>>

\section{Proof of nonexistence of 3-stage Type A ...}

Proof of GSA IMEX schemes of Type~A with 3 stages and the following properties does not exist
\begin{itemize}
  \item Second-order in the streaming limit;
  \item Well-behaved in the diffusion limit;
  \item Positivity-preserving.
\end{itemize}
First of all, the GSA IMEX scheme of Type A with 3 stages have the following form:
\begin{equation*}
  \begin{array}{c | c c c}
  	      0       & 0              & 0              & 0 \\
  	\tilde{c}_{2} & \tilde{a}_{21} & 0              & 0 \\
  	\tilde{c}_{3} & \tilde{a}_{31} & \tilde{a}_{32} & 0 \\ \hline
  	              & \tilde{a}_{31} & \tilde{a}_{32} & 0
  \end{array}
  \qquad
  \begin{array}{c | c c c}
    c_{1} & a_{11} & 0      & 0      \\
  	c_{2} & a_{21} & a_{22} & 0      \\
  	c_{3} & a_{31} & a_{32} & a_{33} \\ \hline
  	      & a_{31} & a_{32} & a_{33}
  \end{array}.
\end{equation*}
The second-order in the streaming limit requires
\begin{align*}
\tilde{a}_{31} + \tilde{a}_{32} = 1, \quad a_{31} + a_{32} + a_{33} = 1, \quad \tilde{a}_{32}\cdot \tilde{a}_{21} =  \frac{1}{2}.
\end{align*}
The diffusion accurate Eq.~\eqref{eq:diffusionCondition} requires 
\begin{align*}
\tilde{a}_{21} = a_{22}, \quad -\dfrac{a_{32} \tilde{a}_{21}}{a_{22}a_{33}} + \dfrac{1}{a_{33}} =1.
\end{align*}
That's 
\begin{align*}
\tilde{a}_{21} = a_{22}, \quad a_{31} = 0.
\end{align*}
Positivity-preserving requires
\begin{align*}
& a_{11} > 0, ~ a_{22} >0, ~ a_{33}>0,\\
& c_{20} = 1 - \frac{a_{21}}{a_{11}} \geq 0, ~ c_{30} = 1-\frac{a_{31}}{a_{11}} + \frac{a_{32}a_{21}}{a_{22}a_{11}} - \frac{a_{32}}{a_{22}}\geq 0, \\
& c_{21} = \frac{a_{21}}{a_{11}} \geq 0, ~ c_{31} = \frac{a_{31}}{a_{11}} - \frac{a_{32}a_{21}}{a_{22}a_{11}} \geq 0, ~ c_{32} = \frac{a_{32}}{a_{22}} \geq 0,\\
& \tilde{c}_{21} = \tilde{a}_{21} \geq 0, \tilde{c}_{31} = \tilde{a}_{31} - \frac{a_{32}\tilde{a}_{21}}{a_{22}} \geq 0, \tilde{c}_{32} = \tilde{a}_{32} \geq 0.
\end{align*}
Note that since $a_{31} = 0$, $a_{21} \geq 0$, $a_{32} \geq 0$, $a_{22} > 0$ and $a_{11} >0$, $c_{31} \geq 0$ only holds for $c_{31} = 0$.
Unfortunately, $c_{31} = 0$ will drag $c_{\mbox{\tiny Sch}} = 0$ since $c_{\mbox{\tiny Sch}} = \min \left\lbrace \dfrac{c_{21}}{\tilde{c}_{21}}, \dfrac{c_{31}}{\tilde{c}_{31}}, \dfrac{c_{32}}{\tilde{c}_{32}}\right\rbrace $.
Therefore, GSA IMEX schemes of Type~A with 3 stages and the above properties does not exist.
